### 2025-07-22 paper/sections/other/main_results.qmd
finished tables

>>>>

## Validity

df_mtbl = aggregate_ce_evaluation(
    mtbl_dir; 
    ratio=true, 
    rebase=false, 
    y="validity", 
    agg_further_vars=["run", "lambda_energy_eval"], 
    total_uncertainty=false, 
    drop_models=["linear"]
)
df_mtbl.variable .= "val"
df = final_table(
    res_dir; 
    ce_var=["validity"],
    agg_further_vars=[["run", "lambda_energy_eval"]],
    tbl_mtbl=df_mtbl
)
Serialization.serialize("paper/experiments/output/validity.jls", df)
```
